Some usefull words/expressions/sentences

### 2018-07-04 phrases.Rmd
toc added

---
title: "Some usefull words/expressions/sentences"
output: html_document
---

@@

#### terry2017discontinuous - Discontinuous Patterns of Cigarette Smoking From Ages 18 to 50 in the United States: A Repeated-Measures Latent Class Analysis

@@

#### lanza2007proc - PROC LCA: A SAS procedure for latent class analysis

@@

#### collins2010latent - Latent Class and Latent Transition Analysis: With Applications in the Social, Behavioral, and Health Sciences

@@

>>>>

---
title: "Some usefull words/expressions/sentences"
output: 
  html_document:
    toc: true
    toc_float: true
---

@@

## terry2017discontinuous

(Discontinuous Patterns of Cigarette Smoking From Ages 18 to 50 in the United States: A Repeated-Measures Latent Class Analysis)

@@

## lanza2007proc

(PROC LCA: A SAS procedure for latent class analysis)

@@

## collins2010latent

(Latent Class and Latent Transition Analysis: With Applications in the Social, Behavioral, and Health Sciences)

@@

- Sometimes fitting a series of latent class models with different numbers of latent classes to data at a single time point can be helpful as a preliminary step in model selection in LTA. Doing this at each time point can be informative about the latent structrue within times, and how that structure changes accross timie points.

- It is important to note that the best-fitting latent class model at any given time may not correspond to the best-fitting latent transition model fit to all occasions of measurements. The best-fitting model based on the data from all occasions of measurement may include a different number of latent stuatuses than the number of latent classes identified at one particular time.

- However, based on the latent status prevalences at each time alone, it is impossible to tell hou and to what extent individuals were moving between latent statuses.

- **In 7.11 we used a different empirical example to test the hypothesis that the item-response probabilities in a LTA are equal across times. This type of restriction on the item-response probabilities is commonly used in LTA. It helps with model identification and, importantly, ensures that the meaning of the latent statuses remains constant over time.**
